---
name: Drew Hughes
headcolor: 414141
params:
  phone: ""
  email: ""
  linkedin: ""
header-includes:
   - \usepackage{enumitem}
output:
  vitae::moderncv:
    theme: classic
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

---
phone: `r params$phone`
email: `r params$email`
linkedin: `r params$linkedin`
---

# Professional Profile
\begin{itemize}[leftmargin = 3 cm]
  \item Clinical Pathology resident applying machine learning to
    complex clinical laboratory data to standardize
    interpretation and increase throughput

  \item MD/PhD scientist with extensive experience developing
    and implementing next-generation sequencing assays and
    bioinformatic analyses

  \item Motivated by opportunities to work with
    multidisciplinary teams using machine learning to build
    next-generation diagnostics and improve patient care

\end{itemize}

\vspace{0 pt}

# Education
```{r, message = FALSE, warning = FALSE}
tribble(
  ~degree, ~institution, ~location, ~dates,
  "MD/PhD, Molecular Genetics and Genomics",
    "Washington University School of Medicine",
    "St. Louis, MO",
    "2009--2019",
  "BS (\\textit{summa cum laude}), Mathematics",
    "College of William \\& Mary",
    "Williamsburg, VA",
    "2004--2008"
) %>%
detailed_entries(
  degree,
  dates,
  institution,
  location,
  .protect = FALSE
)
```

# Work Experience
```{r, message = FALSE, warning = FALSE}
tribble(
  ~position, ~institution, ~location, ~dates, ~details,
  "Resident, Clinical Pathology",
    "Barnes-Jewish Hospital",
    "St. Louis, MO",
    "2019--Present",
    c(
      "Developed machine learning models to automate the 
        interpretation of serum protein electrophoresis to 
        promote result standardization and reduce hands-on 
        time",
      "Performed analysis for the clinical validation of a 
        new molecular test 
        (\\href{https://pathologyservices.wustl.edu/services-tests/chromoseq/}{ChromoSeq})
        and helped prepare the associated documentation",
      "Worked with a multidisciplinary team to build an
        interactive dashboard summarizing respiratory pathogen
        test results to allow clinicians to visualize trends
        over time"
    )
) %>%
detailed_entries(
  position,
  dates,
  institution,
  location,
  details,
  .protect = FALSE
)
```

\vspace{10 pt}

# Research Experience
```{r, message = FALSE, warning = FALSE}
tribble(
  ~position, ~institution, ~location, ~dates, ~details,
  "Graduate Research Thesis",
    "Washington University School of Medicine",
    "St. Louis, MO",
    "2014--2017",
    c(
      "Mapped cell type-specific \\textit{cis}-regulatory elements
        in mouse photoreceptors by performing ATAC-seq and
        RNA-seq on FACS-purified rods and cones",
      "Developed machine learning models to identify sequence
        features associated with photoreceptor-specific regions
        of open chromatin",
      "Designed and implemented a massively parallel reporter
        assay to test quantitative models of
        \\textit{cis}-regulatory element activity
        \\textit{in vivo} at single nucleotide resolution"
    ),
  "Graduate Research Rotation",
    "Washington University School of Medicine",
    "St. Louis, MO",
    "2011",
    "Used targeted single-cell sequencing to reconstruct the
      clonal architecture of tumor specimens from patients with
      secondary acute myeloid leukemia",
  "Undergraduate Research Thesis",
    "College of William \\& Mary",
    "Williamsburg, VA",
    "2006--2008",
    "Characterized patterns of calcium signaling in 
      developing excitatory and inhibitory neurons
      \\textit{in vivo} in the African clawed frog"
) %>%
detailed_entries(
  institution,
  dates,
  position,
  location,
  details,
  .protect = FALSE
)
```

\vspace{10 pt}

# Teaching Experience
```{r, message = FALSE, warning = FALSE}
tribble(
  ~year, ~entry,
  "2015, 2016",
    "\\textbf{Washington University School of Medicine},
    \\textit{Teaching Assistant: Fundamentals of Biostatistics},
    St. Louis, MO",
  "2011",
    "\\textbf{Washington University School of Medicine},
    \\textit{Teaching Assistant: Human Anatomy and Development},
    St. Louis, MO"
) %>%
brief_entries(
  entry,
  year,
  .protect = FALSE
)
```

\vspace{10 pt}

# Skills
```{r, message = FALSE, warning = FALSE}
tribble(
  ~entry,
  "\\textbf{Data Science:} machine learning | statistical 
     modeling | data visualization | R \\{tidyverse\\} 
     \\{tidymodels\\} \\{shiny\\} \\{Bioconductor\\} | Bash 
     | Python | SQL | Git | high-performance computing",
  "\\textbf{Genomics:} next-generation sequencing | nanopore 
      sequencing | end-to-end bioinformatic  analysis | variant
      calling | RNA-seq | ATAC-seq | ChIP-seq | massively 
      parallel reporter assays",
  "\\textbf{Clinical Pathology:}  molecular diagnostics | 
     clinical assay validation | clinical informatics | Epic | 
     Cerner"
) %>%
brief_entries(
  entry,
  .protect = FALSE
)
```

\vspace{10 pt}

# Honors and Awards
```{r, message = FALSE, warning = FALSE}
tribble(
  ~ year, ~ award, ~ department,
  2021,
    "Richard Marshall Education Award",
    "American Association for Clinical Chemistry",
   2021,
    "Clinical Pathology Trainee of the Month",
    "Department of Pathology & Immunology, Washington University
      School of Medicine",
  2021,
    "Best Abstract (Clinical and Diagnostic Immunology)",
    "American Association for Clinical Chemistry",
  2021,
    "Most Innovative Abstract",
    "American Society for Histocompatibility and Immunogenetics",
  2020,
    "Abstract Achievement Award",
    "American Society of Hematology",
  2020,
    "Best Laboratory and Genomic Medicine Grand Rounds 
      Presentation",
    "Department of Pathology & Immunology, Washington University
      School of Medicine",
  2019,
    "Clinical Pathology Trainee of the Month", 
    "Department of Pathology & Immunology, Washington University
      School of Medicine",
  2019,
    "Dr. Philip Rosenblatt Award",
    "Department of Pathology & Immunology, Washington University
      School of Medicine",
  2015,
    "Vision Sciences Training Grant", 
    "Department of Ophthalmology & Visual Sciences, Washington
      University School of Medicine",
  2014,
    "Best Poster", 
    "Molecular Genetics and Genomics/Computational and 
      Systems Biology Annual Retreat, Washington University 
      School of Medicine",
  2008, 
    "Phi Beta Kappa", 
    "College of William & Mary",
  2008, "
    Cissy Patterson Prize", 
    "Department of Mathematics, College of William & Mary",
  2008, 
    "Honors", 
    "Department of Biology, College of William & Mary",
) %>% 
unite("label", c(award, department), sep =",") %>%
mutate(
  label = gsub(",", ", ", label)
) %>%
brief_entries(
  label,
  year
)
```

\vspace{10 pt}

# Peer-Reviewed Publications
```{r, message = FALSE, warning = FALSE}
tribble(
  ~year, ~entry,
  2021,
    "\\textbf{Hughes AEO} and Jackups R Jr. Clinical Decision
    Support for Laboratory Testing.
    \\textit{Clinical Chemistry}, hvab201. Epub ahead of print.
    PMID: 34871351.
    \\url{https://doi.org/10.1093/clinchem/hvab201}",
  2021,
    "Duncavage EJ, Schroeder MC, O'Laughlin M, Wilson R, 
      MacMillan S, Bohannon A, Kruchowski S, Garza J, Du F,
      \\textbf{Hughes AEO}, Robinson J, Hughes E, Heath SE, Baty
      JD, Neidich J, Christopher MJ, Jacoby MA, Uy GL, Fulton 
      RS, Miller CA, Payton JE, Link DC, Walter MJ, Westervelt 
      P, DiPersio JF, Ley TJ, and Spencer DH. Genome Sequencing 
      as an Alternative to Cytogenetic Analysis in Myeloid 
      Cancers. \\textit{The New England Journal of Medicine}, 
      384(10), 924--935. PMID: 33704937. 
      \\url{https://doi.org/10.1056/NEJMoa2024534}",
  2020,
    "Perez-Cervantes C, Smith LA, Nadadur RD, 
      \\textbf{Hughes AEO}, Wang S, Corbo JC, Cepko C, Lonfat N,
      and Moskowitz IP. Enhancer Transcription Identifies 
      \\textit{cis}-Regulatory Elements for Photoreceptor Cell 
      Types. \\textit{Development}, 147(3), dev184432. PMID: 
      31915147. \\url{https://doi.org/10.1242/dev.184432}",
  2020,
    "\\textbf{Hughes AEO}, Webber DM, Wallace MA, Johnson C, 
      Burnham CA, and Anderson NW. Comparable Detections of 
      Viral Pathogens in Lower Respiratory Tract Specimens with 
      the BioFire Respiratory Panel 2 and the BioFire Pneumonia 
      Panel. \\textit{Journal of Clinical Microbiology}, 
      58(6), e00254-20. PMID: 32269103.
      \\url{https://doi.org/10.1128/JCM.00254-20}",
  2020,
    "Volkov LI, Kim-Han JS, Saunders LM, Poria D, 
      \\textbf{Hughes AEO}, Kefalov VJ, Parichy DM, and Corbo 
      JC. Thyroid Hormone Receptors Mediate Two Distinct
      Mechanisms of Long-Wavelength Vision. \\textit{Proceedings 
      of the National Academy of Sciences of the United States 
      of America}, 117(26), 15262--15269. PMID: 32541022.
      \\url{https://doi.org/10.1073/pnas.1920086117}",
  2019,
    "Murphy DP, \\textbf{Hughes AEO}, Lawrence KA, Myers CA, and 
      Corbo JC. \\textit{Cis}-Regulatory Basis of Sister Cell 
      Type Divergence in the Vertebrate Retina. \\textit{Elife}, 
      8, e48216. PMID: 31633482. 
      \\url{https://doi.org/10.7554/eLife.48216}",
  2018,
    "\\textbf{Hughes AEO}, Myers CA, and Corbo JC. A Massively 
      Parallel Reporter Assay Reveals Context-Dependent Activity 
      of Homeodomain Binding Sites In Vivo. 
      \\textit{Genome Research}, 28(10), 1520--1531. PMID:
      30158147.
      \\url{https://doi.org/10.1101/gr.231886.117}",
  2017,
    "\\textbf{Hughes AEO}, Enright JM, Myers CA, Shen SQ, and 
      Corbo JC. Cell Type-Specific Epigenomic Analysis Reveals a 
      Uniquely Closed Chromatin Architecture in Mouse Rod 
      Photoreceptors. \\textit{Scientific Reports}, 7, 43184.
      PMID: 28256534. \\url{https://doi.org/10.1038/srep43184}",
  2016,
    "Shen SQ, Myers CA, \\textbf{Hughes AEO}, Byrne LC, Flannery 
      JG, and Corbo JC. Massively Parallel \\textit{cis}-Regulatory 
      Analysis in the Mammalian Central Nervous System. 
      \\textit{Genome Research}, 26(2), 238--55. PMID: 26576614.
      \\url{https://doi.org/10.1101/gr.193789.115}",
  2015,
    "Young AL, Wong TN, \\textbf{Hughes AEO}, Heath SE, Ley TJ,
      Link DC, and Druley TE. Quantifying Ultra-Rare Pre-Leukemic 
      Clones Via Targeted Error-Corrected Sequencing. 
      \\textit{Leukemia}, 29(7), 1608--11. PMID: 25644247.
      \\url{https://doi.org/10.1038/leu.2015.17}",
  2014,
    "\\textbf{Hughes AEO}, Magrini V, Demeter R, Miller CA, 
      Fulton R, Fulton LL, Eades WC, Elliott K, Heath S, 
      Westervelt P, Ding L, Conrad DF, White BS, Shao J, Link 
      DC, DiPersio JF, Mardis ER, Wilson RK, Ley TJ, Walter MJ, 
      and Graubert TA. Clonal Architecture of Secondary Acute 
      Myeloid Leukemia Defined by Single-Cell Sequencing.
      \\textit{PLOS Genetics}, 10(7), e1004462. PMID: 25010716.
      \\url{https://doi.org/10.1371/journal.pgen.1004462}",
  2012,
    "Ramos E, Levinson BT, Chasnoff S, \\textbf{Hughes AEO}, 
      Young AL, Thornton K, Li A, Vallania FL, Province M, and
      Druley TE. Population-Based Rare Variant Detection Via 
      Pooled Exome or Custom Hybridization Capture with or without 
      Individual Indexing. \\textit{BMC Genomics} 13, 683.
      PMID: 23216810. 
      \\url{https://doi.org/10.1186/1471-2164-13-683}"
) %>%
brief_entries(
  entry,
  year,
  .protect = FALSE
)
```

# Book Chapters
```{r, message = FALSE, warning = FALSE}
tribble(
  ~year, ~entry,
  "2022",
    "Parikh B, \\textbf{Hughes AEO}, and Anderson NW. Molecular 
    Microbiology. \\textit{In Press}"
) %>%
brief_entries(
  entry,
  year,
  .protect = FALSE
)
```

\vspace{10 pt}

# Presentations
```{r, message = FALSE, warning = FALSE}
tribble(
  ~year, ~entry,
  2021,
    "\\textbf{Hughes AEO}, Bell RC, Abel HJ, Schroeder MC, Liu
    C, Duncavage EJ, and Spencer DH. Human Leukocyte Antigen
    Typing of Patients with Myeloid Malignancies by Whole Genome
    Sequencing. Oral presentation, \\textit{Association for
    Molecular Pathology Annual Meeting and Expo}, November
    16-20, Philadelphia, PA",
  2021,
    "\\textbf{Hughes AEO}, Farnsworth CW, and Gronowski AM.
      Automated Interpretation of Serum Protein Electrophoresis.
      Poster presentation,
      \\textit{American Association for Clinical Chemistry},
      September 26--30, Atlanta, GA",
  2021,
    "\\textbf{Hughes AEO}, Montgommery MC, Liu C, and Weimer
      ET. Allele-Specific Quantification of HLA Transcript
      Isoforms by Nanopore Long-Read Sequencing. Poster
      presentation, \\textit{American Society for
      Histocompatibility and Immunogenetics}, September
     27--October 1, Orlando, FL",
  2021,
    "\\textbf{Hughes AEO}, Farnsworth CW, and Gronowski AM.
      Automated Interpretation of Serum Protein Electrophoresis.
      Poster presentation (virtual), 
      \\textit{Association for Pathology Informatics Summit},
      May 18--21, Pittsburgh, PA",
  2020,
    "\\textbf{Hughes AEO}, Montgommery MC, Liu C, and Weimer
      ET. Allele-Specific HLA Expression with Nanopore Long-Read
      Sequencing. Poster presentation (virtual), 
      \\textit{American Society of Hematology Annual Meeting},
      December 5--8, San Diego, CA",
  2020,
    "\\textbf{Hughes AEO}, Webber DM, Wallace MA, Johnson C,
      Burnham CAD, and Anderson NW. Combining the BioFire 
      Pneumonia Panel with Culture Optimizes Lower Respiratory
      Pathogen Testing. Poster presentation (virtual), 
      \\textit{American Society for Microbiology Microbe}, July
      17--18, Chicago, IL",
  2020,
    "\\textbf{Hughes AEO}, Webber DM, Wallace MA, Johnson C,
      Burnham CAD, and Anderson NW. Combining the BioFire 
      Pneumonia Panel with Culture Optimizes Lower Respiratory
      Pathogen Testing. Poster presentation (virtual), 
      \\textit{The Academy of Clinical Laboratory Physicians and 
      Scientists Annual Meeting}, June 25, Iowa City, IA",
  2016,
    "\\textbf{Hughes AEO}, Enright JM, Myers CA, and Corbo
      JC. Nrl mediates widespread changes in the epigenomic 
      landscape of mouse photoreceptors. Poster presentation,
      \\textit{The Biology of Genomes}, May 10--14, Cold Spring 
      Harbor, NY"
) %>%
brief_entries(
  entry,
  year,
  .protect = FALSE
)
```

\vspace{10 pt}

# Peer Review Activities
```{r, message = FALSE, warning = FALSE}
tribble(
  ~year,
  ~entry,
  "2019-2020",
    "Referee: \\textit{Clinical Chemistry},
    \\textit{The Journal of Applied Laboratory Medicine}, and
    \\textit{Journal of Clinical Microbiology}"
) %>%
brief_entries(
  entry,
  .protect = FALSE
)
```